A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-14 src/paper.tex
Adjustments in Web application section

The web applications, which can be hosted in the AHI, comprises the business logic of the second screen application. The content that is presented in the second screen client can be requested through HTTP requests to web services designed for this purpose. In addition, the data captured by second screen clients in the iTV environment can also be sent to the CP by using HTTP requests.

>>>>

The web applications include the business logic, models and controllers that are necessary for the proper functioning of the second screen client application. The content that is presented in the client can be requested through HTTP requests to web services designed for this purpose. In addition, the data captured by second screen clients in the iTV environment can also be sent to the CP by using HTTP requests.
